### 2023-11-22 main.tex
Update main.tex

is the density of specie $a$ and we used the notation $|\alpha|=\sum_{a=1}^{N}\alpha_{a}$. Explicitly, 

@@

If condition \eqref{reversibilityCondition} is not met, then reversibility is lost: each reservoir at site $x$ wants to fix its own set of densities $\rho^{x}=(\rho_{1}^{x},\ldots,\rho_{N}^{x})$ with

@@

@@

\section{Duality}\label{sectionDuality}
In this section we prove the first main result of this paper. We show that the multispecies stirring process with open boundary
can be studied by means of a dual process. After recalling the definition of duality between two
Markov processes in Section \ref{def-duality}, we formulate duality  in Theorem \ref{thm-duality}. A proof of the theorem is given in Section \ref{proof-th-duality}.
The duality result is important since it brings in several simplifications, the main one being that the
dual process has absorbing sites. Therefore, as shown in Proposition \ref{prop-absorbing}, the study of the non-equilibrium steady state for  the multispecies stirring process with open boundary
is reduced to the study of the absorption probabilities of dual particles.

@@

when the state spaces of the dual processes is countable, the generators of the processes and the duality function can be represented as matrices with elements $\mathcal{L}(\eta,\eta')$, $\widetilde{\mathcal{L}}(\xi,\xi')$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta'\in\Omega$ and $\xi,\xi'\in \widetilde{\Omega}$. Therefore, we can write the duality relation \eqref{dualityRelationGenerator} as 

@@

	The multi-species stirring process $(\bm{n}(t))_{t\geq 0}$ defined on the state space $\Omega$ with generator $\mathcal{L}$ defined in \eqref{Generator} is dual to a process $(\bm{\xi}(t))_{t\geq 0}$ defined on the enlarged state space $\widetilde{\Omega}$ with generator

@@

where we have introduced the reservoir densities

@@

\begin{remark} in the reversible situation, i.e. when $\forall x\in V$ we have $\rho_{a}^{x}=\rho_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{\text{rev}} = \bigotimes_{x\in V}\text{Multinomial}\left(\twoj, \rho_{1},\ldots,\rho_{N}\right)$ is

@@

\subsection{Duality for the integrable process on a line segment}\label{integrableChain-duality}
Here we consider the chain defined in Section \ref{subsection-description-process-LINE} with the hard-core constrain, i.e. $\nu=1$. 
We recall that the geometry is a one dimensional chain with sites $\{1,\ldots,L\}$ where reservoirs are attached to $1$ and $L$. 
We also recall the notation for the occupation variable which is called $\bm{\tau}=(\tau_1,\ldots,\tau_L)$ with $\tau_x\in\{1,\ldots,N\}$.
The dynamics is described by an Hamiltonian that is written in terms of the first fundamental representation of $gl(N)$. The duality result stated in Section \ref{statementDualitySubsection} can be adapted. The extra-sites are denoted by $0$ and $L+1$, and they are connected with sites $1$ and $L$ of the chain respectively. The matrix $R_{x}$ defined in \eqref{Revmatrix} 
reduces to the identity, therefore the relation between the generators of the algebra and its transposed reduces to
\begin{equation}\label{transpostionPropertyFund}
	e_{ab}^T= e_{ba}\dt
\end{equation}
Therefore, duality matrix reads
\begin{equation}
	D=\mathcal{D}_{0}\otimes\prod_{x=1}^{L}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\otimes \mathcal{D}_{L+1}
\end{equation}
where $\mathcal{D}_{0}$ and $\mathcal{D}_{L+1}$ are given in \eqref{dualityMatrix2}. 
The elements of this duality matrix are given by
\begin{equation}\label{ElementsDualityMatrixChain_1}
	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
\end{equation}
%\begin{equation}\label{ElementsDualityMatrixChain}
%	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{n_{a}^{x}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
%\end{equation}
The dual Hamiltonian is
\begin{equation}
	\widetilde{H}=\widetilde{H}_{\text{left}}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+\widetilde{H}_{\text{right}}
\end{equation}
where $\mathcal{H}$ is defined in \eqref{H-corsivo} and 
\begin{equation}\label{boundary-H-dual-chain}
	\widetilde{H}_{\text{left}}=\sum_{a=1}^{N-1}\left((\mathbf{a}^{+})_{a}^{0}\,e_{Na}^{1}-e_{aa}^{1}\right)\qquad 	\widetilde{H}_{\text{right}}=\sum_{a=1}^{N-1}\left((\mathbf{a}^{+})_{a}^{L+1}\,e_{Na}^{L}-e_{aa}^{L}\right)\dt
\end{equation}
In the long-time limit the dual process voids the chain, i.e. all particles of types $\{1,\ldots,N-1\}$ are eventually absorbed at the extra-sites $0$ and $L+1$ and replaced by types $N$. We also notice that, up the the bosonic creation operators $(\mathbf{a}^{+})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular. This simplification will be crucial in Section \ref{sectionIntegrabiliy}.\\

@@

Using duality, one can compute the  $m$-point correlations between non-empty particles in terms of the absorption probabilities of $m$ dual particles. Therefore, to determine the non-equilibrium steady state correlations of the integrable multi-species stirring process, it is enough to compute these absorption probabilities. In the following we denote by $\mu$ the non-equilibrium steady state distribution. %For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$. 

@@

Consider $m\in \{1,\ldots,L\}$ and let $a_{k}\in\{1,\ldots,N-1\}$ species positioned at sites $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$. Then, the $m$-point correlations in the non-equilibrium steady state (NESS) read

@@

\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})

@@

is the  probability that  $t_{k}$ dual particles of species $a_{k}$ (initially positioned at site $x_{k}$) are absorbed at the extra site $\{0\}$. The dual initial configuration is $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 

@@

@@

Therefore, by duality and ergodicity we have 

@@

\mathbb{E}_{\mu}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{\tau_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]

@@

@@

	The result written in the previous Corollary \ref{prop-absorbing} holds also for chains with higher maximal occupancy ($\nu>1)$, as specified in Section \ref{Subsection-ss-nonI}. 

@@

    \begin{corollary}[Non-equilibrium steady state measure]\label{Corollary-NESS-ABS}
For any configuration $\bm{\tau}\in \Omega^{'}$ the non-equilibrium steady state probability mass function is given by 
	\mu(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{q}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{b}}=1}^{N-1}\mathbb{E}_{\mu}\left[\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\prod_{k=1}^{b}\mathbbm{1}_{\{\sigma_{q_{k}}=a_{q_{k}}\}}\right]
where the expectation, computed with respect to the process $\bm{\sigma}$, is given in \eqref{NESS-expectation-ABS} in terms of absorption probabilities. 
\textbf{Proof of \ref{Corollary-NESS-ABS}:}
Consider a generic $\bm{\tau}\in \Omega^{'}$, then we have 
	\mu\left(\bm{\tau}\right)=&\mathbb{E}_{\mu}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right]
	=\mathbb{E}_{\mu}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{\sigma_{x}=N\}}\right)\right]\nonumber\\
	=&\mathbb{E}_{\mu}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a_{x}\}}\right)\right)\right]
\begin{equation}			\mathbbm{1}_{\{\sigma_{x}=N\}}=1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a_{x}\}}\dt
The configuration $\bm{\tau}$ has $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$ occupied sites and then the remaining $L-\ell$ are empty. % We introduce an index $b\in \{0,\ldots,L-\ell\}$. 
Then, we rewrite the argument of the expectation above as
&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{\sigma_{x}=a_{x}\}}\right)\right)\nonumber\\
\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}+\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)(-1)\left\{\sum_{q_{1}=1}^{L}\delta_{\tau_{q_{1}},N}\sum_{a_{q_{1}}=1}^{N-1}\mathbbm{1}_{\{\sigma_{q_{1}}=a_{q_{1}}\}}\right\}+\nonumber\\
+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)(-1)^{2}\left\{\sum_{1\leq q_{1}<q_{2}\leq L}\delta_{\tau_{q_{1}},N}\delta_{\tau_{q_{2}},N}\sum_{a_{q_{1}},a_{q_{2}}=1}^{N-1}\mathbbm{1}_{\{\sigma_{q_{1}}=a_{q_{1}}\}}\mathbbm{1}_{\{\sigma_{q_{2}}=a_{q_{2}}\}}\right\}+\ldots+\nonumber\\
+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)(-1)^{L-\ell}\sum_{1\leq q_{1}<\ldots<q_{L-\ell}\leq L}\left(\prod_{k=1}^{L-\ell}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{L-\ell}}=1}^{N-1}\prod_{k=1}^{L-\ell}\mathbbm{1}_{\{\sigma_{q_{k}}=a_{q_{k}}\}}\dt

>>>>

is the density of species $a$ and we used the notation $|\alpha|=\sum_{a=1}^{N}\alpha_{a}$. Explicitly, 

@@

If condition \eqref{reversibilityCondition} is not met, then in general reversibility is lost (but see remark \ref{rem-rev} below): 
each reservoir at site $x$ wants to fix its own set of densities $\rho^{x}=(\rho_{1}^{x},\ldots,\rho_{N}^{x})$ with

@@

\label{rem-rev}
		One can check that the following condition on the reservoir parameters implies reversibility:
		\label{cond-gen}
			\alpha_{k}^{x}\left(|\alpha^{y}|-\alpha_{k}^{y}\right)=\alpha_{k}^{y}\left(|\alpha^{x}|-\alpha_{k}^{x}\right)\qquad\qquad \forall x,y\in V,\quad \forall k\in \{1,\ldots,N\}
			|\alpha^{x}|=\sum_{a=1}^{N}\alpha_{a}^{x}\dt
		This is slightly more general than \eqref{reversibilityCondition}. In the case where the graph is a chain with nearest neighbors interactions and two reservoirs are attached to the two boundary sites
		then condition \eqref{cond-gen} is the multi-species counterpart of $\alpha\delta=\beta\gamma$ of the boundary driven partially excluded process introduced in \cite{schutzSandow} (see Section 3.2 of \cite{carinci2013duality}).

@@

\section{Duality}\label{sectionDuality}
In this section we prove the first main result of this paper. We show that the multispecies stirring process with open boundary
can be studied by means of a dual process. After recalling the definition of duality between two
Markov processes in Section \ref{def-duality}, we formulate our duality result  in Theorem \ref{thm-duality}. A proof of the theorem is given in Section \ref{proof-th-duality}.
The duality result is important since it yields several simplifications, the main one being that the
dual process has absorbing sites. Therefore, as shown in Corollary \ref{prop-absorbing}, the study of correlations in the non-equilibrium steady state of the multispecies stirring process with open boundary
is reduced to the study of the absorption probabilities of dual particles.

@@

When the state spaces of the dual processes is countable, the generators of the processes and the duality function can be represented as matrices with elements $\mathcal{L}(\eta,\eta')$, $\widetilde{\mathcal{L}}(\xi,\xi')$ and $D(\eta,\xi)$ for arbitrary $\eta,\eta'\in\Omega$ and $\xi,\xi'\in \widetilde{\Omega}$. Therefore, we can write the duality relation \eqref{dualityRelationGenerator} as 

@@

	The multi-species stirring process $(\bm{n}(t))_{t\geq 0}$ defined on the state space $\Omega$ with generator $\mathcal{L}$ defined in \eqref{Generator} is dual to the process $(\bm{\xi}(t))_{t\geq 0}$ defined on the enlarged state space $\widetilde{\Omega}$ with generator

@@

where we recall the definition of the reservoir densities (cf. \eqref{rhox})

@@

\begin{remark} In the reversible situation, i.e. when $\forall x\in V$ we have $\rho_{a}^{x}=\rho_{a}$, the expectation  of the duality function  $D(\bm{n},\bm{\xi})$ with   $\bm{n}$ distributed as  $\mu_{\text{rev}} = \bigotimes_{x\in V}\text{Multinomial}\left(\twoj, \rho_{1},\ldots,\rho_{N}\right)$ is

@@

\subsection{Duality for the integrable process on a line segment}\label{integrableChain-duality}
Here we consider the chain defined in Section \ref{subsection-description-process-LINE} with the hard-core constrain, i.e. $\nu=1$. 
We recall that the geometry is a one dimensional chain with sites $\{1,\ldots,L\}$ where reservoirs are attached to $1$ and $L$. 
We also recall the notation for the occupation variable which is called $\bm{\tau}=(\tau_1,\ldots,\tau_L)$ with $\tau_x\in\{1,\ldots,N\}$.
The dynamics is described by an Hamiltonian that is written in terms of the first fundamental representation of $gl(N)$. The duality result stated in Section \ref{statementDualitySubsection} is adapted to the present situation as follows. 
The extra-sites are denoted by $0$ and $L+1$, and they are connected with sites $1$ and $L$ of the chain respectively. The matrix $R_{x}$ defined in \eqref{Revmatrix} 
reduces to the identity, therefore the relation between the generators of the algebra and its transposed reduces to
\begin{equation}\label{transpostionPropertyFund}
	e_{ab}^T= e_{ba}\dt
\end{equation}
Therefore, duality matrix reads
\begin{equation}
	D=\mathcal{D}_{0}\otimes\prod_{x=1}^{L}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\otimes \mathcal{D}_{L+1}
\end{equation}
where $\mathcal{D}_{0}$ and $\mathcal{D}_{L+1}$ are given in \eqref{dualityMatrix2}. 
The elements of this duality matrix are given by
\begin{equation}\label{ElementsDualityMatrixChain_1}
	D(\bm{\tau},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\tau_{x},a}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
\end{equation}
%\begin{equation}\label{ElementsDualityMatrixChain}
%	D(\bm{n},\bm{\xi})=\prod_{a=1}^{N-1}\alpha_{a}^{\xi_{a}^{0}}\left(\prod_{x=1}^{L}\prod_{a=1}^{N-1}\mathbbm{1}_{\{n_{a}^{x}\geq \xi_{a}^{x}\}}\right)\prod_{a=1}^{N-1}\beta_{a}^{\xi_{a}^{L+1}}\dt
%\end{equation}
The dual Hamiltonian is
\begin{equation}
	\widetilde{H}=\widetilde{H}_{\text{left}}+\sum_{x=1}^{L-1}\mathcal{H}_{x,x+1}+\widetilde{H}_{\text{right}}
\end{equation}
where $\mathcal{H}$ is defined in \eqref{H-corsivo} and 
\begin{equation}\label{boundary-H-dual-chain}
	\widetilde{H}_{\text{left}}=\sum_{a=1}^{N-1}\left((\mathbf{a}^{+})_{a}^{0}\,e_{Na}^{1}-e_{aa}^{1}\right)\qquad 	\widetilde{H}_{\text{right}}=\sum_{a=1}^{N-1}\left((\mathbf{a}^{+})_{a}^{L+1}\,e_{Na}^{L}-e_{aa}^{L}\right)\dt
\end{equation}
In the long-time limit the dual process voids the chain, i.e. all particles of types $\{1,\ldots,N-1\}$ are eventually absorbed at the extra-sites $0$ and $L+1$ and replaced by types $N$. We also notice that, up the the bosonic creation operators $(\mathbf{a}^{+})_{a}$, the dual boundary Hamiltonians \eqref{boundary-H-dual-chain} are triangular. This simplification will be crucial in Section \ref{sectionIntegrabiliy}.\\

@@

Using duality, one can compute the  $m$-point correlations between non-empty particles in terms of the absorption probabilities of $m$ dual particles. Therefore, to determine the non-equilibrium steady state correlations of the integrable multi-species stirring process, it is enough to compute these absorption probabilities. In the following we denote by $\mu$ the non-equilibrium steady state distribution and we call $\bm{Y} = (Y_1,\ldots,Y_L)$ the random vector with law $\mu$. 
Furthermore we write $\mathbb{E}[\cdot]$ for the expectation with respect to $\mu$.%For arbitrary $m\in \mathbb{N}$ such that $m<L$, we fix $a_{k}\in\{1,\ldots,N-1\}$ and $x_{k}\in\{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for every $k\in\{1,\ldots,m\}$. 

@@

Let $m\in \{1,\ldots,L\}$ and consider $m$ sites $1 \le x_{1} < x_2 < \ldots < x_m \le L $ and
$m$ species $a_{k}\in\{1,\ldots,N-1\}$  with $k=1,2,\ldots, m$. Then, the $m$-point correlations in the non-equilibrium steady state read

@@

\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]=\sum_{t_{1}=0}^{1}\ldots \sum_{t_{m}=0}^{1}\prod_{k=1}^{m}\alpha_{a_{k}}^{t_{k}}\beta_{a_{k}}^{1-t_{k}}\mathcal{P}_{x_1,\ldots,x_m}(t_{1},\ldots,t_{m})

@@

where the initial dual configuration is $\bm{\xi}=\sum_{k=1}^{m}\delta_{a_{k}}^{x_{k}}$, meaning that 

@@

In \eqref{absProbabilitiesIntegrable} the variable $t_k$ is $1$ (resp. $0$) when the dual particle of species $a_k$ initially positioned at site $x_{k}$ is absorbed at at the extra site $\{0\}$ (resp. $\{L+1\}$).

@@

Therefore, by ergodicity and duality  we have 

@@

\mathbb{E}\left[\prod_{k=1}^{m}\mathbbm{1}_{\{Y_{x_{k}}=a_{k}\}}\right]&=\lim_{t\to \infty}\mathbb{E}_{\bm{\tau}}\left[D(\bm{\tau}(t),\bm{{\xi}})\right]=\lim_{t\to \infty}\mathbb{E}_{\bm{\xi}}\left[D(\bm{\tau},\bm{{\xi}}(t))\right]

@@

    \begin{corollary}[Non-equilibrium steady state]\label{Corollary-NESS-ABS}
For any configuration $\bm{\tau}\in \Omega^{'}$  the probability mass function of the non-equilibrium steady states is given by 
	\mu(\bm{\tau})=\sum_{b=0}^{L}(-1)^{b}\sum_{1\leq q_{1}<\ldots<q_{b}\leq L}\left(\prod_{k=1}^{b}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{b}}=1}^{N-1}
	\mathbb{E}\left[\left( \prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right) \left(\prod_{k=1}^{b}\mathbbm{1}_{\{Y_{q_{k}}=a_{q_{k}}\}}\right)\right]\,.
\textbf{Proof of Corollary \ref{Corollary-NESS-ABS}:}
Given $\bm{\tau}\in \Omega^{'}$,  we have 
	\mu\left(\bm{\tau}\right)=&\mathbb{E}\left[\prod_{x=1}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right]
	=\mathbb{E}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_x\}}\right)\right]\nonumber\\
	=&\mathbb{E}\left[\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_{x}=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{Y_{x}=a_{x}\}}\right)\right)\right]
	%\\=&\sum_{\bm{\sigma}\in \Omega^{'}}\prod_{x=1}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\langle \bm{\sigma}|\Psi\rangle\nonumber\\
	%	=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\mathbbm{1}_{\{Y_x=N\}}\right)\langle\bm{\sigma}|\Psi\rangle\nonumber\\
	%	=&\sum_{\bm{\sigma}\in \Omega^{'}}\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{i_{x}=1}^{N-1}\mathbbm{1}_{\{Y_x=i_{x}\}}\right)\langle\bm{\sigma}|\Psi\rangle
\begin{equation}			\mathbbm{1}_{\{Y_{x}=N\}}=1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{Y_{x}=a_{x}\}}\dt
The configuration $\bm{\tau}$ has $\ell=\sum_{x=1}^{L}(1-\delta_{\tau_{x},N})$ occupied sites and then the remaining $L-\ell$ sites are empty. % We introduce an index $b\in \{0,\ldots,L-\ell\}$. 
Therefore, we may write
&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)\left(\prod_{x=1\,:\,\tau_{x}=N}^{L}\left(1-\sum_{a_{x}=1}^{N-1}\mathbbm{1}_{\{Y_x=a_{x}\}}\right)\right)\nonumber\\
\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}+\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)\left\{\sum_{q_{1}=1}^{L}\delta_{\tau_{q_{1}},N}\sum_{a_{q_{1}}=1}^{N-1}\mathbbm{1}_{\{\sigma_{q_{1}}=a_{q_{1}}\}}\right\}+\nonumber\\
+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)^{2}\left\{\sum_{1\leq q_{1}<q_{2}\leq L}\delta_{\tau_{q_{1}},N}\delta_{\tau_{q_{2}},N}\sum_{a_{q_{1}},a_{q_{2}}=1}^{N-1}\mathbbm{1}_{\{Y_{q_{1}}=a_{q_{1}}\}}\mathbbm{1}_{\{Y_{q_{2}}=a_{q_{2}}\}}\right\}+\ldots+\nonumber\\
+&\left(\prod_{x=1\,:\,\tau_{x}\neq N}^{L}\mathbbm{1}_{\{Y_x=\tau_{x}\}}\right)(-1)^{L-\ell}\sum_{1\leq q_{1}<\ldots<q_{L-\ell}\leq L}\left(\prod_{k=1}^{L-\ell}\delta_{\tau_{q_{k}},N}\right)\sum_{a_{q_{1}},\ldots,a_{q_{L-\ell}}=1}^{N-1}\prod_{k=1}^{L-\ell}\mathbbm{1}_{\{Y_{q_{k}}=a_{q_{k}}\}}\dt

@@

	The results in Corollary \ref{Corolollary-ABS_Corr-abstract} and in Corollary \ref{Corollary-NESS-ABS}  can be generalized to arbitrary graphs $G=(V,\mathcal{E})$ and for higher maximal occupancies $\nu >1$.
	However the computation of absorption probabilities of the dual process is possible only in the set-up of the integrable chain with $\nu =1$ and two reservoirs at the boundaries.
	Thus we chose to present them in such a context.

@@

\section{Correlations and steady state  for the integrable chain}\label{sectionIntegrabiliy}
In this section we combine duality and the matrix product ansatz (MPA) to charaterize the non-equilibrium steady state for the integrable version of the multi-species stirring process, defined in Section \ref{integrableChain-duality}. 
As it will turn out, such combination of duality and MPA allows to determine a closed formula for the absorption probabilities and thus (using Corollary \ref{Corolollary-ABS_Corr-abstract}) for the correlations
and (using Corollary \ref{Corollary-NESS-ABS}) for the probability mass-function of the non-equilibrium steady state.
We start by recalling the formulation of the MPA  and then we explain our strategy.

\subsection{Matrix product ansatz for the non-equilibrium steady state}
The matrix product ansatz for the multi-species stirring process has been formulated in \cite{vanicat2017exact}, here we briefly recall the main steps.
 Denoting by $|\Psi(t)\rangle$ the column vector that encodes the probability distribution of the chain with Hamiltonian \eqref{hamiltonian} at time $t\geq 0$, its evolution equation is given by 
 the master equation
\begin{equation}
    \frac{d|{\Psi}(t)\rangle}{dt}=H|{\Psi}(t)\rangle\dt
\end{equation}
This Markov chain is irreducible and positive recurrent, therefore there exists a unique stationary measure, that will be reached when time goes to infinity, regardless of the initial configuration. 
We denote by $|\Psi\rangle$ the column vector that gives the stationary distribution (non-equilibrium steady state). This vector is the right eigenvector with vanishing eigenvalue of $H$, i.e. it solves 
\begin{equation}\label{definition-SteadyStateH}
	H|\Psi\rangle =0\dt
\end{equation}
The MPA states the following
\begin{equation}
	|\Psi\rangle=\frac{1}{Z_{L}}\langle W|\begin{pmatrix}
		X_{1}\\
		\vdots\\
		X_{N}
	\end{pmatrix}\otimes \ldots\otimes \begin{pmatrix}
		X_{1}\\
		\vdots\\
		X_{N}
	\end{pmatrix}|V\rangle
\end{equation}
with the normalization 
\begin{equation}
	Z_{L}=\langle W|(X_{1}+\ldots +X_{N})^{L}|V\rangle\dt
\end{equation}
Here the operators $(X_{a})_{a\in \{1,\ldots,N\}}$ fulfil the commutators
\begin{equation}\label{bulk}
	\left[X_{a},X_{b}\right]=(\alpha_{a}-\beta_{a})X_{b}-(\alpha_{b}-\beta_{b})X_{a}%\qquad\forall a,b=1,\ldots,N
\end{equation}
and their action on the boundary vectors are
\begin{equation}\label{leftBoundary}
	\langle W|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=(\alpha_{a}-\beta_{a})\langle W|%\qquad\forall a=1,\ldots,N\co
\end{equation}
\begin{equation}\label{rightBoundary}
	\left(\beta_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)|V\rangle=-(\alpha_{a}-\beta_{a})|V\rangle%\qquad\forall a=1,\ldots,N\dt
\end{equation}
Without loss of generality, we further assume that $\langle W|V\rangle=1$. 
\begin{remark} Only $N-1$ of the $N$ equations \eqref{leftBoundary}  are independent. This can be seen by summing them over the species $a\in \{1,\ldots,N\}$, i.e.
	\begin{equation}
		\sum_{a=1}^{N}	\langle W|\left(\alpha_{a}(X_{1}+\ldots+X_{N})-X_{a}\right)=0,%\sum_{a=1}^{N}(\alpha_{a}-\beta_{a})\langle W|=0
	\end{equation}
	and using  \eqref{ratesConditions}.
 Similarly for the right boundary  \eqref{rightBoundary} there are only  $N-1$ independent equations. \end{remark} 
The MPA gives an abstract form of the non-equilibrium steady state in terms of an algebra of operators. However, the computation of  correlations are in general involved.

\subsection{Strategy}
 In the next Section \ref{subsection-exact} we will show that the existence of the absorbing dual process established in Section \ref{sectionDuality} simplifies substantially the algebra of operators $X_a$ defined in previous
 section.  The idea is summarized in the following scheme. 
